Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-01-04 SI.tex
Fix the number of materials

Due to time-consuming simulations and significant increment in 
memory overload, high-accurate calculations at hybrid HSE06 level is limited 
to about 56 compounds. 
It is desirable to validate our proposed
relations on an even larger scale database. We select over 230
semiconducting 2D materials from Ref.~\citenum{Haastrup_2018} 
with a GW bandgap
larger than 0.05 eV and extracted the 2D polarizabilities calculated
on the PBE level. The proposed linear relations between
$1/\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and
$\alpha_{\mathrm{2D}}^{\perp}-\delta_{\mathrm{cov}}$ are also valid,
as shown in Figure \ref{fig:gpaw-alpha-relation}. Excellent linear
correlation is observed in both cases with the $R^{2}$ coefficient
larger than 0.9 which indicates the existence of a universal description 
of 2D dielectric nature through the proposed relations with the 2D
polarizabilities. We note that the slope of the linear regression is
slightly different from the one proposed from the dielectric
response at the HSE06 level.

>>>>

Due to time-consuming simulations and significant increment in 
memory overload, high-accurate calculations at hybrid HSE06 level is limited 
to about 55 compounds. 
It is desirable to validate our proposed
relations on an even larger scale database. We select over 230
semiconducting 2D materials from Ref.~\citenum{Haastrup_2018} 
with a GW bandgap
larger than 0.05 eV and extracted the 2D polarizabilities calculated
on the PBE level. The proposed linear relations between
$1/\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and
$\alpha_{\mathrm{2D}}^{\perp}-\delta_{\mathrm{cov}}$ are also valid,
as shown in Figure \ref{fig:gpaw-alpha-relation}. Excellent linear
correlation is observed in both cases with the $R^{2}$ coefficient
larger than 0.9 which indicates the existence of a universal description 
of 2D dielectric nature through the proposed relations with the 2D
polarizabilities. We note that the slope of the linear regression is
slightly different from the one proposed from the dielectric
response at the HSE06 level.
